Welcome to the Proceedings of the first iteration of the Big Picture Workshop (The Big Picture: Crafting a Research Narrative). The workshop is hosted at EMNLP 2023, in Singapore, on December 7, 2023. 
\\\\
The Big Picture Workshop provides a dedicated venue for exploring and distilling broader NLP research narratives. All research exists within a larger context, and progress is made by standing on the shoulders of giants: building on the foundations laid by earlier researchers. In light of rapid publication rates and concise paper formats, it has become increasingly difficult, however, to recognize the larger story to which a paper is connected. The Big Picture Workshop invites researchers to reflect on how their individual contributions fit within the overall research landscape and what stories they are telling with their bodies of research. The goals of the workshop are to enhance communication and understanding between different lines of work, highlight how works connect and build on each other, generate insights that are difficult to glean without combining and reconciling different research narratives, encourage broader collaboration and awareness of prior work in the NLP community, and facilitate understanding of trajectories and insights within the field of NLP.
\\\\
We received 12 submissions, of which we accepted 10 for presentation at the workshop. Those 10 accepted papers are contained in this volume. We also accepted for presentation two additional papers to be included in Findings of EMNLP 2023.
\\\\
The workshop schedule features one standard invited talk, and three special invited presentations designed to foster live engagement between different lines of related work. In these special presentations, two to three invited presenters speak on their individual lines of work and the connections between them, followed by a moderated discussion further exploring the overall narrative that emerges from these works in aggregate. In addition to invited presentations, the workshop features one Best Paper session, one in-person poster session, and one virtual poster session.
\\\\
We extend heartfelt thanks to our program committee, our participants, and all authors who submitted papers for consideration---your engagement has been critical to the success of the workshop. We also thank Amazon, Google, and Hugging Face for generous sponsorship. Finally, we thank the EMNLP 2023 organizers for their hard work and support. 
\\\\\\\\
The Big Picture Workshop Organizers,
\\\\
Yanai Elazar, Allyson Ettinger, Nora Kassner, Sebastian Ruder, Noah Smith
